
\clearpage
\section{Limitations and Monitoring}
This section documents known limits of this synthetic audit scenario and the monitoring posture that should accompany any customer deployment.

\paragraph{Synthetic quality is advisory in this run.}
The synthetic-quality certificate reports a threshold of \SqThresholdUsed{} and an observed score of \SqScore{}. In this scenario the threshold is \ifnum\SqThresholdMet>0 met\else not met\fi, and the results should be interpreted as an evidence-backed \emph{audit} rather than a blanket compliance claim.

\paragraph{Small-group visibility for race.}
Race uncertainty is displayed in the main text only when all race groups exceed minimum size and proportion thresholds. In this run, the observed minimum group size is \RaceObservedMinGroupN{} and minimum proportion is \RaceObservedMinGroupPct{}, so race is gated to the appendix/annex views when the display policy is not satisfied.

\paragraph{Data coverage, label noise, and covariate shift.}
The synthetic scenario exercises a defined lending-audit fixture. It does not prove coverage of every geography, product line, credit policy, or protected-class intersection that may appear in a production portfolio. Operators should review data dictionaries, missingness, label provenance, and segment coverage before treating a customer run as deployment evidence. Material distribution drift or label-policy changes should trigger a rerun.

\paragraph{Monitoring plan.}
Customer deployments should define control limits for the primary fairness metric, approval-rate gaps, data-quality checks, and evidence-chain validity before production use. Retraining, threshold changes, feature-policy changes, or sustained drift beyond those limits should trigger governance review and fresh evidence generation.
